New lower bounds for Schur and weak Schur numbers

### 2022-02-24 article/soumission_SIAM/article.tex
dossier siam
sauv-siam

\documentclass[3p]{elsarticle}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{dsfont}
\usepackage{MyMnSymbol}

\usepackage[english]{babel}
\usepackage[hyphens]{url}
\usepackage[hidelinks]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{siunitx}
\usepackage{float}

\usepackage[table]{xcolor}
\usepackage{multirow}
\usepackage{nicematrix}

@@

\newtheorem{definition}{Definition}[section]
\newtheorem{notation}[definition]{Notation}
\newtheorem{theorem}[definition]{Theorem}
\newtheorem{computational theorem}[definition]{Computational Theorem}
\newtheorem{corollary}[definition]{Corollary}
\newtheorem{remark}[definition]{Remark}
\newtheorem{proposition}[definition]{Proposition}

@@

\author[1]{Romain Ageron\fnref{fn1}}
\ead{romain.ageron@student-cs.fr}

\author[1]{Paul Casteras\fnref{fn1}}
\ead{paul.casteras@student-cs.fr}

\author[1]{Thibaut Pellerin\fnref{fn1}}
\ead{thibaut.pellerin@student-cs.fr}

\author[1]{Yann Portella\fnref{fn1}}
\ead{yann.portella@student-cs.fr}

\author[2]{Arpad Rimmel\fnref{fn2}}
\ead{arpad.rimmel@centralesupelec.fr}

\author[2]{Joanna Tomasik\corref{cor1}\fnref{fn2}}
\ead{joanna.tomasik@centralesupelec.fr}

\cortext[cor1]{Corresponding author}
\fntext[fn1]{These authors contributed equally.}
\fntext[fn2]{These authors supervised the work of the main authors.}

\address[1]{CentraleSup\'elec, Universit\'e{} Paris-Saclay, 91 190, Gif-sur-Yvette, France}
\address[2]{LISN, CentraleSup\'elec, Universit\'e{} Paris-Saclay, 91 405, Orsay, France}

@@

\begin{keyword}
Schur number \sep Weak Schur number \sep Ramsey theory \sep Sum-free partition
\MSC[2020]{05D10 \sep 05A17 \sep 11B75 \sep 11B81}
\end{keyword}

@@

\bibliography{biblio}
\bibliographystyle{elsarticle-num.bst}

\include{appendix.tex}

\end{document}

>>>>

\documentclass[review,onefignum,onetabnum]{siamart190516}

%\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{amsthm}
\usepackage{dsfont}
\usepackage{MyMnSymbol}

%\usepackage[english]{babel}
%\usepackage[hyphens]{url}
%\usepackage[hidelinks]{hyperref}
%\usepackage[utf8]{inputenc}
%\usepackage{siunitx}
\usepackage{float}

%\usepackage[table]{xcolor}
\usepackage{multirow}
\usepackage{nicematrix}

@@

\newsiamremark{remark}{Remark}

@@

%\author[1]{Romain Ageron\fnref{fn1}}
%\ead{romain.ageron@student-cs.fr}

%\author[1]{Paul Casteras\fnref{fn1}}
%\ead{paul.casteras@student-cs.fr}

%\author[1]{Thibaut Pellerin\fnref{fn1}}
%\ead{thibaut.pellerin@student-cs.fr}

%\author[1]{Yann Portella\fnref{fn1}}
%\ead{yann.portella@student-cs.fr}

%\author[2]{Arpad Rimmel\fnref{fn2}}
%\ead{arpad.rimmel@centralesupelec.fr}

%\author[2]{Joanna Tomasik\corref{cor1}\fnref{fn2}}
%\ead{joanna.tomasik@centralesupelec.fr}

%\cortext[cor1]{Corresponding author}
%\fntext[fn1]{These authors contributed equally.}
%\fntext[fn2]{These authors supervised the work of the main authors.}

%\address[1]{CentraleSup\'elec, Universit\'e{} Paris-Saclay, 91 190, Gif-sur-Yvette, France}
%\address[2]{LISN, CentraleSup\'elec, Universit\'e{} Paris-Saclay, 91 405, Orsay, France}

@@

%\begin{keyword}
%Schur number \sep Weak Schur number \sep Ramsey theory \sep Sum-free %partition
%\MSC[2020]{05D10 \sep 11P81 \sep 05A17 \sep 11B75}
%\end{keyword}

@@

\bibliography{biblio}
\bibliographystyle{siamplain}

\include{appendix.tex}
\end{document}
